### 2016-03-08 README.Rmd
fix #516 changes to many fxns, all rank values to lower, fixed tests accordingly

```{r install_stable, eval=FALSE}
install.packages("taxize")
```

@@

```{r install_dev, eval=FALSE}
install.packages("devtools")
devtools::install_github("taxize", "ropensci")
```

```{r load}
library('taxize')
```

@@

@@

+ [Scott Chamberlain](https://github.com/sckott)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Karthik Ram](https://github.com/karthik)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)

>>>>

```{r eval=FALSE}
install.packages("taxize")
```

@@

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropensci/taxize")
```

```{r}
library('taxize')
```

@@

## Lowest common rank among taxa

```{r lowest}
spp <- c("Sus scrofa", "Homo sapiens", "Nycticebus coucang")
lowest_common(spp, db = "ncbi")
```

@@

+ [Scott Chamberlain](https://github.com/sckott)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Karthik Ram](https://github.com/karthik)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
+ [James O'Donnell](https://github.com/jimmyodonnell)
+ [Francois Michonneau](https://github.com/fmichonneau)
+ [Philippe Marchand](https://github.com/pmarchand1)
+ [Jari Oksanen](https://github.com/jarioksa)
+ [Oliver Keyes](https://github.com/Ironholds)
+ [Luis Villanueva](https://github.com/ljvillanueva)
+ [David LeBauer](https://github.com/dlebauer)
+ [Ben Marwick](https://github.com/benmarwick)
